### 2022-09-28 NSF2022/Description/specificaim1.tex
starting proposal

\section{Proposed Research}
\label{sec:proposed-work}
%%

\subsection{Specific Aim 1: Measuring material properties of amphiphile
  self-assembly}
\label{subsec:specific_aim_1}
Specific Aim 1 proposes a novel mathematical model for particle
self-organization driven by long-range interfacial forces. 
The research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.
Applications in this area include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-changes
\cite{McBr21, HaBr20}.

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/Domain.jpg}
 \caption{\label{fig:flow_map}
   In the HAP formulation,
   a system of exterior problems 
   defines the hydronamic and hydrophobic interactions.
   The colormap is for the intensity of $u$.
   The dynamics lead to self-organized structures like a vesicle bilayer.}
\end{wrapfigure}

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. We then use a
second-order Adams-Bashforth method to update the particle configuration.
Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional takes the form 
\begin{equation}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{equation}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

\begin{wrapfigure}[10]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/3Particles.jpg}
 \caption{\label{fig:3particles}
   \footnotesize
   Particles translate and rotate to lower the free energy $F[u]$
   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
   The arrows are the velocity field $\mathbf{u}$.
 }
\end{wrapfigure}
The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

%By solving the above system, we obtain translational and angular
%velocities of the many-body system. A second-order Adams-Bashforth
%scheme updates the particle positions and orientations.

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time-step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently.

%and
%\begin{equation}
%  \label{eq:force}
%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
%  \dif s = T_i, \qquad i=1,\ldots,N_b,
%\end{equation}
%where
%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
%particle outward normal.

\subsubsection{Janus-particle self-assembly} 
Distinct morphologies can be obtained from 
the HAP model by shifting the boundary condition $g$.
Consider the linear case where $f(u) = u^2$.
This choice makes \eqref{eq:SL} a boundary value
problem for the screened-Laplace equation
and the solutions have a boundary layer structure that decays to $0$ in the
bulk with the decay length $\rho$.
We consider three kinds of boundary conditions
on particle $\Gamma_i$:
\begin{equation}
  \label{eq:bcs}
  \begin{tabular}{c|c|c}
     \text{(a)} & \text{(b)} & \text{(c)} \\
    \hline
    \rule{0pt}{4ex} 
      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
\end{tabular}
\end{equation}
  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
of radius $r$. 
The cases (b) and (c) are obtained by applying a vertical shift
and scaling to case (a), see Figure \ref{fig:bcs}.
Using this setup, we simulate the dynamics of 100 particles with random
initial position and orientation.

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}
Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[13]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, long time.
  }
\end{wrapfigure}
Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

Finally, boundary condition \eqref{eq:bcs}(c) models 
a particle whose head surface repels the tail surface as proposed in
\cite{MaRa76, Ma77}.
The particles initially form chains with their directors perpendicular to the
length of the chain. The equilibrium structure
resembles a checkerboard pattern
where each particle coordinates
its head with the head of three other particles and its tail with the
tail of three other particles Figure~\ref{fig:self-assembly}(c).

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control surface properties independently, 
which can be difficult to accomplish experimentaly 
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density function for 
relative orientation of adjacent particles
for the three boundary condition cases:
(a) is unimodal with a peak at $\theta = 0$,
(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
This kind of information can be used as an indicator
of the collective morphology. As another example,
it is costly or difficult to manufacture
Janus particles with uniform shape.
Thus, we can replace the idealistic boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function is asymptotic to a normal distribution with variance
like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example.

\subsubsection{Hydrophobic forces with double-well potential}
A natural generalization of the potential $f(u) = u^2$
is a fourth-order, asymmetric double-well potential
$f(u) = a(u-u_0)^2(u-u_1)^2 + c(u-u_0)^2 + bu$.
Here, the order parameter $u$ is related to
the mean number of nearest neighbors
per water molecule \cite{GoHaKo94}.
The value $u_0$ gives the absolute minimum in the bulk
and $u_1$ gives a local minimum at hydrophobic surfaces.
Figure \ref{fig:CA}(a) illustrates a double-well potential.

\begin{wrapfigure}[29]{l}{1.8in}
  \vspace{-4pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} (a) The double well potential $u_0 =
  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
  and inexact Newton's methods.}
\end{wrapfigure}
Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example.
PI BQ has developed fast integral equation solvers for
the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
PI RR has experience in the 
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
%The proposed research develops fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
%%
We have demonstrated that our hydrophobic attraction with repulsion
potential (HAP) approach efficiently simulates self-assembly of
amphiphilic particles into two-dimensional micelles, bilayer membranes,
and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
phenomenon in external shear flows \cite{FuQuRyYo20}.
While the results show great promise in the field of collective body
hydrodynamics, several outstanding issues need to be addressed. These
include a thorough analysis of elastic properties of our coarse-grained
bilayers and efficiently simulating three-dimensional collective
hydrodynamics of amphiphilic particles.
We must also incorporate electric charge and account
for how external fields control particle self-assembly. 
%mathematically
%characterize the variational behavior of HARP under appropriate
%homogenized limits.

\subsection{Specific Aim 1: Measuring material properties of amphiphile self-assembly}
\label{subsec:specific_aim_1}

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
%\end{center}
%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
%\label{fig:distortions}
%\end{figure}
The goal of Specific Aim 1 is to characterize the material properties of
many-body, self-assembled amphiphiles.  For amphiphiles assembled into
bilayers, these properties are described by membrane continuum
mechanics.  Our goal is to map the parameters of the particle-based
model onto the elastic moduli from continuum theory.  Results from this
goal will facilitate simulators to use the hydrophobic attraction force
calculations to model bilayers with specific composition. These
calculations have provably less computational complexity than those of
molecular dynamics simulations and possess the molecular granularity
lacking from continuum models.

Hamm and Kozlov (HK) pioneered the modern theory of membrane continuum
mechanics~\cite{Hamm2000}, and their theory is widely used to describe
biological phenomena, including fission \cite{FrEsAkSh15, Maetal15,
PhysRevE.79.031926}, fusion \cite{ChKo08,
KoKo2002,Kuzmin7235,Aeffner2012}, poration~\cite{Gaetal20}, phase
boundaries, and interaction with inclusions~\cite{SeLeMaEg17,Saetal20,
Pietal20}. These phenomena require resolution of the internal structure
of the membrane.  Recently, there has been a revival of interest in the
HK theory as the quadratic assumption for the elasticity energy density
has caused researchers to question the applicability of the theory for
large curvatures~\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.46\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

%\begin{wrapfigure}[13]{l}{0.5\textwidth}
%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
%diaphragm expansion (ii) and pore formation (iii). 
%(B) Saddle-splay energy for each change in \emph{monolayer} topology
%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
%\label{fig:barriers}
%\end{wrapfigure}

\sloppy
The HK framework assumes a three-dimensional lipid monolayer where the internal structure
consists of straight fibers that represent elongated hydrocarbon chains.
The elastic energy density ${\cal W}$ is quadratic in the Green-Lagrange strain
tensor for this striated, internal structure.
%
%
%
%These fibers
%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
%Accordingly, the deformation takes the form 
%\begin{equation}
%  \label{LMdeformation}
%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
%\end{equation}
%where $(X_1,X_2,X_3)$ are points in a reference volume.
%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
%
%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
%The chains stretch and compress to satisfy incompressibility.
%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
%lead to an elastic surface energy over the dividing surface $\Sigma$. 
%
This energy density decomposes into four, fundamental, and independent
deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
the unit surface normal;
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, 
%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
%Also, the surface divergence 
%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
%respectively (Figure \ref{fig:distortions}A--C).
the deformations come with elastic coefficients: the bending modulus
$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
$\KTH$.
%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
%
The parameter $k_0$ is the spontaneous curvature and determines the
preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
%As an illustration, the
%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
%%as a result of  %having a relatively long acyl chain. 
%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
%because the addition of a positive splay 
%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
%The subtraction of $k_0^2$ makes the energy distortion free
%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.

Although the HK elastic theory assumes small deformations, 
Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
Under spatial scales much larger than the membrane thickness, membrane
energy is well-characterized by the Canham-Helfrich energy used
throughout the fluid-structure literature \cite{QiangDu09,
Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014,
qua-vee-you2019}. The Canham-Helfrich energy is actually a special case
of \eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the
$\pm$ depending on orientation) and collapsing both monolayers onto the
membrane midplane.
%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
%are equal to zero.

%\begin{figure}
%\begin{center}
%\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
%\end{center}\vspace{-1.em}
%\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
%The quartic fit comes from continuum theory. 
%(B) A circular vesicle at equilibrium. (C) The area modulus derives
%from convexity in energy as a function of radius. 
%\label{fig:bend}}
%\end{figure}

% Proposers should address what they want to do,
% why they want to do it,
% how they plan to do it,
% how they will know if they succeed,
% and what benefits could accrue if the project is successful.
%\begin{center}
%Preliminary results
%\end{center}

%\begin{wrapfigure}[13]{l}{0.5\textwidth}
%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
%diaphragm expansion (ii) and pore formation (iii). 
%(B) Saddle-splay energy for each change in \emph{monolayer} topology
%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
%\label{fig:barriers}
%\end{wrapfigure}

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HAP model to estimate elastic moduli
and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
\begin{wrapfigure}[11]{r}{0.43\textwidth}
%\vspace{-0.4cm}
\centerline{\includegraphics[width=0.42\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
%\vspace{-0.5cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
We propose to {\bf (i)} determine the value of effective elastic moduli
$\KB$, $\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the
model parameters $\rho,$ $\gamma$, and the particle shape map onto
elastic moduli. An accurate and robust way to measure material
properties is to track the evolution of the bilayer as it relaxes from
an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}.
Figure~\ref{fig:flattening} shows an example where the initial
configuration of a bilayer patch containing the splay deformation
without any other components (saddle splay, twist and tilt). As the bent
membrane flattens, both the self-interaction energy $\Phi$ and the
elastic energy ${\cal W}$ decrease, and because the saddle splay, twist,
and tilt stay zero, the slope gives the bending modulus in this case.

%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
%We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
%$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
%%
%%Motivated by our preliminary results \cite{Fu2018_SIAM}
%%we use realistic values for particle diameter $2$ nm \cite{Boal},
%%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
%%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
%%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
%%particle diameter and the hydrophobic boundary condition \eqref{SL}
%%are additional parameters defining the coarse-grained representation. 
%
%An accurate and robust way to measure material properties is to track the evolution of the bilayer.

Here we start with a particle-based bilayer in a specific
non-equilibrium shape that involves only one of the components of the
displacement in Figure~\ref{fig:deformations}, and then evolve the
particle system according to the time integration for \eqref{eq:stokes}.
Because elastic properties are independent of dissipation, we can forgo
solving for fluid velocity and set the translational velocity and
angular velocity directly proportional to the force and torque,
respectively. 
%bilayer by steepest gradient descent 
%with respect to the HARP functional:
%\begin{equation}
%\label{SGD}   
%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
%\end{equation}
%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
%The procedure involves solving \eqref{SL} based off of the current particle configuration.
%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
%through \eqref{SGD}.
%

This yields a dissipation of the total potential \eqref{eq:total_poten}, which
stabilizes the evolving bilayer shape.
Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.

%In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
%When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
%and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.

%
%Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
%The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
%the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
%energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
%Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
%These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
%as required by fussion and fission. 
%
%Bending is the energetically most consequential deformations. To measure a bending modulus,  
%we deform the midplane of a planar bilayer into the shape of a circular arc.
%This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
%The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
%In the case of a rectangular bialyer, the corresponding elastic energy 
%$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
%Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
%used to values for infer $\KB$.

%
We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
for other elastic moduli such as the effective twist modulus $\KT$.
Molecular dynamics investigations find a twist modulus about 1
\kBT~\cite{LeVeWa14}, and here, the specific non-equilibrium shape consists of
a single layer of amphiphilic particles on a hydrophobic substrate as
illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
requires nonzero tilt because the surface gradient of the lipid
director equals the second fundamental form
%, and is therefore symmetric,
whenever tilt is zero locally. The twist deformation is a fully
three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
